### 2025-06-03 manuscript.Rmd
fix missing space added ethics statement

authornote: |
  Please address correspondence to: Andreas M. Brandmaier, Rüdesheimer Str. 50, 14197 Berlin, Germany. Email: andreas.brandmaier@medicalschool-berlin.de.
  The R package described in this article can be downloaded from https://github.com/brandmaier/reproducibleRchunks. The manuscript source code is available at https://github.com/brandmaier/reproducibleRchunks-manuscript. We thank Julia Delius forher helpful assistance in language and style editing. We also thank Leonie Hagitte for providing comments on an earlier version of the manuscript.

@@

classoption       : "man" #man
output            : papaja::apa6_pdf
#output            : papaja::apa6_docx
header-includes:
   - \usepackage{amsmath}  # providing non-breaking mbox environment
---

@@

Now, we define a reproducible code chunk by setting the code chunk language to `reproducibleR`. 
Once this document is rendered for the first time, a data file will be created that stores all reproducible results computed in this code block. 
The name of the file will contain the label name (in this example `helloworld`). 
The following code block contains two reproducible results stored in variables `x` and `y`. 
Those computations can be based on results computed in previous chunks but those variables will not be subject to the reproducibility tests _per se_.
If the R markdown document is rendered a second time, the computational results are recomputed and compared against the original results. 
For each result, reproduction success or failureis reported separately.

@@

>>>>

authornote: |
  Please address correspondence to: Andreas M. Brandmaier, Rüdesheimer Str. 50, 14197 Berlin, Germany. Email: andreas.brandmaier@medicalschool-berlin.de.
  The R package described in this article can be downloaded from https://github.com/brandmaier/reproducibleRchunks. The manuscript source code is available at https://github.com/brandmaier/reproducibleRchunks-manuscript. We thank Julia Delius for her helpful assistance in language and style editing. We also thank Leonie Hagitte for providing comments on an earlier version of the manuscript.

@@

classoption       : "man" #man
output            : papaja::apa6_pdf
#output            : papaja::apa6_docx
keeptex           : yes
header-includes:
   - \usepackage{amsmath}  # providing non-breaking mbox environment
---

@@

Now, we define a reproducible code chunk by setting the code chunk language to `reproducibleR`. 
Once this document is rendered for the first time, a data file will be created that stores all reproducible results computed in this code block. 
The name of the file will contain the label name (in this example `helloworld`). 
The following code block contains two reproducible results stored in variables `x` and `y`. 
Those computations can be based on results computed in previous chunks but those variables will not be subject to the reproducibility tests _per se_.
If the R markdown document is rendered a second time, the computational results are recomputed and compared against the original results. 
For each result, reproduction success or failure is reported separately.

@@

# Ethics statement

This study did not involve testing of human participants.
